Reaction & action alternatives

### 2023-05-30 01_studies/01_Laborstudie ProVisioNET/R script/action alternatives/reaction_action_alternatives.Rmd
action alt. r code
Update reaction_action_alternatives.Rmd

# creating new column with total reactions
main_novice <- main %>%
  filter(id %in% c("Novice")) %>% 
  mutate(reaction_sum = sum(reaction),
         nd_sum = sum(nd),
         sum = sum(n()),
         percent_reaction = round((reaction_sum/sum),
                                  digits = 2),
         percent_nd = round((nd/count),
                            digits = 2)
         )

# creating new column with total reactions
main_expert <- main %>%
  filter(id %in% c("Expert")) %>% 
  mutate(reaction_sum = sum(reaction),
         nd_sum = sum(nd),
         sum = sum(n()),
         percent_reaction = round((reaction_sum/sum),
                                  digits = 2),

@@

@@

>>>>

# creating new column with total reactions
main_novice <- main %>%
  filter(id %in% c("Novice")) %>% 
  mutate(reaction_sum = sum(reaction),
         nd_sum = sum(nd),
         sum_participants = sum(n()),
         percent_reaction = round((reaction_sum/sum_participants),
                                  digits = 2),
         percent_nd = round((nd/count),
                            digits = 2)
         )

# creating new column with total reactions
main_expert <- main %>%
  filter(id %in% c("Expert")) %>% 
  mutate(reaction_sum = sum(reaction),
         nd_sum = sum(nd),
         sum_participants = sum(n()),
         percent_reaction = round((reaction_sum/sum_participants),
                                  digits = 2),

@@

# effect size for expertise differences
CohenD(x = main$percent_nd[main$id == "Expert"],
       y = main$percent_nd[main$id == "Novice"],
       na.rm = TRUE)

@@

# correlation: count x efficacy
